---
title: "Introduction to SA23204177"
author: "Mingming Xiang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SA23204177}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SA23204177__ is a simple R package developed to test whether the sample mean vector is a zero vector (Wang and Shao, 2020) using R, Rcpp and RcppEigen (implemented through the R package _Rcpp_ and _RcppEigen_).
Both R and Rcpp versions are produced. Namely _Wang2020_ for R and _Wang2020C_ for C++.

The R package 'microbenchmark' can be used to benchmark the above R and C++ functions.

## Details
Suppose we have a $p$-dimensional stationary nonlinear time series
$Y_t=\mu+g(\epsilon_t,\epsilon_{t-1},\cdots)$, for some measurable function $g$, where $\{\epsilon_t\}_{t=-\infty}^\infty$ are i.i.d. random elements in some measurable space. 

For $r \in [0,1]$, define 
$$
T_n(r):=\sum_{t=1}^{\lfloor nr\rfloor}\sum_{s=1}^tY_{t+m}^TY_s.
$$
The test statistic is defined as:
$$
T_{SN,n}:=\frac{T_n(1)^2}{W_n^2},
$$
where $W_n^2=\frac1n\sum_{k=1}^n\left(T_n(k/n)-\frac{k(k+1)}{n(n+1)}T_n(1)\right)^2$.


## Source code of _Wang2020_ and _Wang2020C_

The source R code for _Wang2020_ is as follows:
```{r,eval=FALSE}
T_n <- function(r,n1,YY,m){
  t_n = 0
  n = floor(r*n1)
  for (t in 1:n){
    t_n = t_n + sum(YY[t+m,1:t])
  }
  return(t_n)
}

Wang2020 <- function(sam,m,n){
  n1 = n-m
  YY = sam%*%t(sam)
  W <- NULL
  for (k in 1:n1){
    W[k] = (T_n(k/n1,n1,YY,m)-k*(k+1)/n1/(n1+1)*T_n(1,n1,YY,m))^2
  }
  W_n = mean(W)
  test = T_n(1,n1,YY,m)^2/W_n
  reject = test > 54.70
  return(reject)
}
```


The source C++ code for _Wang2020C_ is as follows:
```{Rcpp,eval=FALSE}
#include <RcppEigen.h>
using namespace Rcpp;
// [[Rcpp::depends(RcppEigen)]]
//[[Rcpp::export]]
double T_nC(double r, int n1, const Eigen::MatrixXd& YY, int m){
  double t_n = 0;
  int n = r*n1;
  for (int i=1; i<=n; i++){
    for (int j=1; j<=i; j++){
      t_n = t_n + YY(i+m-1,j-1);
    }
  }
  return t_n;
}

//[[Rcpp::export]]
bool Wang2020C(const Eigen::MatrixXd& sam, int m, int n){
  double n1 = n - m;
  Eigen::MatrixXd YY = sam * sam.adjoint();
  double W = 0;
  for (int k=1; k <= n1; k++){
    W += pow(T_nC(k/n1,n1,YY,m)-k*(k+1)/n1/(n1+1)*T_nC(1,n1,YY,m),2);
  }
  double W_n = W / n1;
  double test = pow(T_nC(1,n1,YY,m),2)/W_n;
  bool reject = test > 54.70;
  return reject;
}
```


## Examples

```{r}
library(SA23204177)
library(MASS)
set.seed(1234)
n1 <- n2 <- 50
p <- 200
mu1 <- rep(0, p)
mu2 <- mu1
mu2[1:10] <- 1
true.cov <- 0.4^(abs(outer(1:p, 1:p, "-"))) # AR1 covariance
sam1 <- mvrnorm(n = n1, mu = mu1, Sigma = true.cov)
sam2 <- mvrnorm(n = n2, mu = mu2, Sigma = true.cov)
Wang2020(sam1, m=5, n=n1)
Wang2020(sam2, m=5, n=n2)
Wang2020C(sam1, m=5, n=n1)
Wang2020C(sam2, m=5, n=n2)
```

## Benchmarking _Wang2020_ and _Wang2020C_

```{r,eval=TRUE}
library(microbenchmark)

tm2 <- microbenchmark(
  Wang2020 = Wang2020(sam1, m=5, n=n1),
  Wang2020C = Wang2020C(sam1, m=5, n=n1)
)
knitr::kable(summary(tm2)[,c(1,3,5,6)])
```

The above results show an evident computational speed gain of C++ against R.



